---
title: "Estimating Error in Measurements of Sox2 Locus Tracking"
author: "Jeff Alexander"
date: "6/25/2017"
output: html_document
---
###Live Cells/Low SNR
###Estimating error in XY Measurements by streaming images of cuO/cymR spot
####(which should have a separation distance of 0 nm)
####Error from 1) Shot noise 2) Movement between frames

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(MASS)
source('~/Library/Mobile Documents/com~apple~CloudDocs/Scripts/R/Scripts/Rfunctions.R')
load("~/Library/Mobile Documents/com~apple~CloudDocs/Batch42_streaming.RData")
```

```{r}
images <- unique(Batch42_streaming$C1_Image)
for (i in images){
  cur_data = Batch42_streaming[Batch42_streaming$C1_Image == i,];
  for (j in 1:200){
    if (nrow(cur_data[cur_data$C1_T.Value..frame. == (j - 1),]) != 0 && nrow(cur_data[cur_data$C1_T.Value..frame. == j,]) != 0){
    cur_data[cur_data$C1_T.Value..frame. == j, "XY_Streaming Distance (um)"] <- sqrt((cur_data[cur_data$C1_T.Value..frame. == (j - 1), "C1_X.Value..um."] - cur_data[cur_data$C1_T.Value..frame. == j, "C1_X.Value..um."])^2 + (cur_data[cur_data$C1_T.Value..frame. == (j - 1), "C1_Y.Value..um."] - cur_data[cur_data$C1_T.Value..frame. == j, "C1_Y.Value..um."])^2);
    }
  }
  Batch42_streaming[Batch42_streaming$C1_Image == i, "XY_Streaming Distance (um)"] <- cur_data$`XY_Streaming Distance (um)`
}



hist(Batch42_streaming$`XY_Streaming Distance (um)`, breaks=50)
```

```{r}
x_error <- Batch42_streaming

x_vals <- seq(0, 5, by=0.01)
##XY error
gp <- ggplot_setup(TRUE)
gp <- gp + geom_density(data=x_error, aes(`XY_Streaming Distance (um)`), color="grey", fill="grey", alpha=0.3, size=1.0) + scale_x_continuous(limits=c(0,0.5), breaks=c(0, 0.1, 0.2, 0.3, 0.4, 0.5)) + xlab("XY Distance (um)") + ylab("Normalized Density") + theme(axis.line.x = element_line(size=1.2, color="white"), axis.line.y = element_line(size=1.2, color="white")) + scale_y_continuous(limits=c(0,15), breaks=c(0, 5, 10, 15))
gp
```
```{r}
er_dens <- density(x_error$`XY_Streaming Distance (um)`, na.rm=TRUE)
mode_xlocation <- er_dens$x[er_dens$y == max(er_dens$y)]
mode_y <- max(er_dens$y)
gp <- ggplot_setup(TRUE)
gp <- gp + geom_density(data=x_error, aes(`XY_Streaming Distance (um)`), color="grey", fill="grey", alpha=0.3, size=1.0) + scale_x_continuous(limits=c(0,0.5), breaks=c(0, 0.1, 0.2, 0.3, 0.4, 0.5)) + xlab("XY Distance (um)") + ylab("Normalized Density") + theme(axis.line.x = element_line(size=1.2, color="white"), axis.line.y = element_line(size=1.2, color="white")) + scale_y_continuous(limits=c(0,15), breaks=c(0, 5, 10, 15))
gp <- gp + geom_segment(aes(x=mode_xlocation, y=0, xend=mode_xlocation, yend=mode_y), linetype="dashed", color="white")
gp <- gp + geom_text(aes(x = mode_xlocation + 0.005, y=mode_y + 0.1, label=c("Mode (48 nm)")), color="white", angle=45, hjust="left", size=4)
gp
```

###Fixed Cells/High SNR
###Estimating error in XY Measurements by streaming images of cuO/cymR spot
####(which should have a separation distance of 0 nm)
####Error from 1) Shot noise 2) Movement between frames
```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(MASS)
source('~/Library/Mobile Documents/com~apple~CloudDocs/Scripts/R/Scripts/Rfunctions.R')
load("~/Library/Mobile Documents/com~apple~CloudDocs/Batch50_03_streaming.Rdata")
```


```{r}
Batch50_03_streaming <- data.frame(BatchXX_data_combined_pairs_trackmate, "XY_Streaming.Distance..um."=NA)
head(Batch50_03_streaming)
```

```{r}
images <- unique(Batch50_03_streaming$C1_Image)
for (i in images){
  cur_data = Batch50_03_streaming[Batch50_03_streaming$C1_Image == i,];
  for (j in 1:200){
    if (nrow(cur_data[cur_data$C1_T.Value..frame. == (j - 1),]) != 0 && nrow(cur_data[cur_data$C1_T.Value..frame. == j,]) != 0){
    cur_data[cur_data$C1_T.Value..frame. == j, "XY_Streaming.Distance..um."] <- sqrt((cur_data[cur_data$C1_T.Value..frame. == (j - 1), "C1_X.Value..um."] - cur_data[cur_data$C1_T.Value..frame. == j, "C1_X.Value..um."])^2 + (cur_data[cur_data$C1_T.Value..frame. == (j - 1), "C1_Y.Value..um."] - cur_data[cur_data$C1_T.Value..frame. == j, "C1_Y.Value..um."])^2);
    }
  }
  Batch50_03_streaming[Batch50_03_streaming$C1_Image == i, "XY_Streaming.Distance..um."] <- cur_data$`XY_Streaming.Distance..um.`
}



hist(Batch50_03_streaming$`XY_Streaming.Distance..um.`, breaks=50)
```

```{r}
x_error <- Batch50_03_streaming

x_vals <- seq(0, 5, by=0.01)
##XY error
gp <- ggplot_setup(TRUE)
gp <- gp + geom_density(data=x_error, aes(`XY_Streaming.Distance..um.`), color="grey", fill="grey", alpha=0.3, size=1.0) + scale_x_continuous(limits=c(0,0.5), breaks=c(0, 0.1, 0.2, 0.3, 0.4, 0.5)) + xlab("XY Distance (um)") + ylab("Normalized Density") + theme(axis.line.x = element_line(size=1.2, color="white"), axis.line.y = element_line(size=1.2, color="white")) + scale_y_continuous(limits=c(0,70), breaks=c(0, 5, 10, 15, 20, 25))
gp
```
```{r}
er_dens <- density(x_error$`XY_Streaming.Distance..um.`, na.rm=TRUE)
mode_xlocation <- er_dens$x[er_dens$y == max(er_dens$y)]
mode_y <- max(er_dens$y)
gp <- ggplot_setup(TRUE)
gp <- gp + geom_density(data=x_error, aes(`XY_Streaming.Distance..um.`), color="grey", fill="grey", alpha=0.3, size=1.0) + scale_x_continuous(limits=c(0,0.5), breaks=c(0, 0.1, 0.2, 0.3, 0.4, 0.5)) + xlab("XY Distance (um)") + ylab("Normalized Density") + theme(axis.line.x = element_line(size=1.2, color="white"), axis.line.y = element_line(size=1.2, color="white")) + scale_y_continuous(limits=c(0,70), breaks=c(0, 5, 10, 15, 20, 25))
gp <- gp + geom_segment(aes(x=mode_xlocation, y=0, xend=mode_xlocation, yend=mode_y), linetype="dashed", color="white")
gp <- gp + geom_text(aes(x = mode_xlocation + 0.005, y=mode_y + 0.1, label=paste("Mode (", round(mode_xlocation * 1000), " nm)", sep = "")), color="white", angle=45, hjust="left", size=4)
gp
```

###Live Cells/High SNR
###Estimating error in XY Measurements by streaming images of cuO/cymR spot
####(which should have a separation distance of 0 nm)
####Error from 1) Shot noise 2) Movement between frames
```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(MASS)
source('~/Library/Mobile Documents/com~apple~CloudDocs/Scripts/R/Scripts/Rfunctions.R')
load("~/Library/Mobile Documents/com~apple~CloudDocs/Batch50_06_streaming.Rdata")
```


```{r}
Batch50_06_streaming <- data.frame(BatchXX_data_combined_pairs_trackmate, "XY_Streaming.Distance..um."=NA)
head(Batch50_06_streaming)
```

```{r}
images <- unique(Batch50_06_streaming$C1_Image)
for (i in images){
  cur_data = Batch50_06_streaming[Batch50_06_streaming$C1_Image == i,];
  for (j in 1:200){
    if (nrow(cur_data[cur_data$C1_T.Value..frame. == (j - 1),]) != 0 && nrow(cur_data[cur_data$C1_T.Value..frame. == j,]) != 0){
    cur_data[cur_data$C1_T.Value..frame. == j, "XY_Streaming.Distance..um."] <- sqrt((cur_data[cur_data$C1_T.Value..frame. == (j - 1), "C1_X.Value..um."] - cur_data[cur_data$C1_T.Value..frame. == j, "C1_X.Value..um."])^2 + (cur_data[cur_data$C1_T.Value..frame. == (j - 1), "C1_Y.Value..um."] - cur_data[cur_data$C1_T.Value..frame. == j, "C1_Y.Value..um."])^2);
    }
  }
  Batch50_06_streaming[Batch50_06_streaming$C1_Image == i, "XY_Streaming.Distance..um."] <- cur_data$`XY_Streaming.Distance..um.`
}



hist(Batch50_06_streaming$`XY_Streaming.Distance..um.`, breaks=50)
```

```{r}
x_error <- Batch50_06_streaming

x_vals <- seq(0, 5, by=0.01)
##XY error
gp <- ggplot_setup(TRUE)
gp <- gp + geom_density(data=x_error, aes(`XY_Streaming.Distance..um.`), color="grey", fill="grey", alpha=0.3, size=1.0) + scale_x_continuous(limits=c(0,0.5), breaks=c(0, 0.1, 0.2, 0.3, 0.4, 0.5)) + xlab("XY Distance (um)") + ylab("Normalized Density") + theme(axis.line.x = element_line(size=1.2, color="white"), axis.line.y = element_line(size=1.2, color="white")) + scale_y_continuous(limits=c(0,70), breaks=c(0, 5, 10, 15, 20, 25))
gp
```
```{r}
er_dens <- density(x_error$`XY_Streaming.Distance..um.`, na.rm=TRUE)
mode_xlocation <- er_dens$x[er_dens$y == max(er_dens$y)]
mode_y <- max(er_dens$y)

gp <- ggplot_setup(TRUE)
gp <- gp + geom_density(data=x_error, aes(`XY_Streaming.Distance..um.`), color="grey", fill="grey", alpha=0.3, size=1.0) + scale_x_continuous(limits=c(0,0.5), breaks=c(0, 0.1, 0.2, 0.3, 0.4, 0.5)) + xlab("XY Distance (um)") + ylab("Normalized Density") + theme(axis.line.x = element_line(size=1.2, color="white"), axis.line.y = element_line(size=1.2, color="white")) + scale_y_continuous(limits=c(0,70), breaks=c(0, 5, 10, 15, 20, 25))
gp <- gp + geom_segment(aes(x=mode_xlocation, y=0, xend=mode_xlocation, yend=mode_y), linetype="dashed", color="white")
gp <- gp + geom_text(aes(x = mode_xlocation + 0.005, y=mode_y + 0.1, label=paste("Mode (", round(mode_xlocation * 1000), " nm)", sep = "")), color="white", angle=45, hjust="left", size=4)
gp
```
